%# -*- coding: utf-8-unix -*-
\begin{thanks}

I would like to thank my advisor, Prof. Cewu Lu, for his guidance in the field of machine learning and computer vision. I joined his lab in my junior year, and since then I worked under his guidance, where two fruitful years have passed. Without Prof. Cewu Lu, I can never have such comprehensive knowledge in machine learning and computer vision. Prof. Cewu Lu also provided me with many information happening on the frontiers of this field, and substantial career suggestions. During the conduction of this project, we had fruitful discussions twice every week. I would not have completed this project without his help. I would also like to thank the members in MVIG lab led by Prof. Cewu Lu, in which we discussed new papers and shared ideas often.

I would also like to thank my first academic advisor, Prof. Ying Cui. It was your patient supervision that led me to the world of research during my sophomore year in university. Without your careful revision on the paper, I could not have published my first research project, and have such ample research experience to pursue more difficult research questions.

Thanks also to my roommates, Zheng Luo, Fuming Zhang and Zheng Luo. We spent the most time together in the dormitory, and it was your understanding to provide me with the best atmosphere to study and help each other.

Last but not least, I would like to thank my family. It was your encouragement when I felt depressed. It was your kind reminder when I was not focused on work. Without your support and love, I could not have the achievements I achieved today.

\end{thanks}
